\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{array}
\usepackage{parskip}

\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue, citecolor=blue}

\title{Retrieval and Classification of the Scientific Literature on the\\
Capacitated Arc Routing Problem: A Reproducible Pipeline}
\author{CARP review project}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
This document describes the methodology used to systematically collect, classify, and
analyse the body of scientific publications on the Capacitated Arc Routing Problem
(CARP), its structural variants, and its solution methodology. The pipeline has three
main stages: (1) automated metadata retrieval from the OpenAlex bibliographic
aggregator, (2) rule-based classification of each article's CARP variant and solution
approach through a structured keyword taxonomy, and (3) semantic classification with a
large language model (LLM) that assigns a single primary label per article and
summarises how the problem was solved. The resulting corpus covers 905 unique works
(1981--2026); a focused subset of 206 works published from 2021 onward is used for
the main analysis.
\end{abstract}

\tableofcontents
\newpage

% ------------------------------------------------------------------ %
\section{Overview}
% ------------------------------------------------------------------ %

The pipeline has four sequential stages:

\begin{enumerate}[nosep]
  \item \textbf{Collection.} The OpenAlex REST API is queried with a set of carefully
        chosen search phrases that cover the CARP, its major structural variants, and
        its principal solution methodologies. For each retrieved work only metadata are
        stored---no full texts or PDFs are downloaded.
  \item \textbf{Rule-based classification.} A deterministic keyword classifier
        analyses the concatenated title and abstract of each article to assign variant
        labels and a solution-approach category. The classifier applies structured
        regular-expression taxonomies and is fully transparent and reproducible.
  \item \textbf{LLM semantic classification.} A large language model re-reads each
        abstract and assigns a single primary variant and a single primary solution
        method, together with a relevance judgement and a one-sentence description of
        how the problem was solved.
  \item \textbf{Analysis.} The LLM-classified corpus is summarised through a set of
        figures (publication trends, variant and method distributions, open-access
        share) and a variant-by-approach cross-tabulation.
\end{enumerate}

All intermediate and final outputs are stored in both CSV and JSON formats to
facilitate re-use and manual inspection.

% ------------------------------------------------------------------ %
\section{Data source and rationale}
% ------------------------------------------------------------------ %

A central design decision of the pipeline is to \emph{not} scrape publisher websites
directly. Direct scraping of platforms such as Elsevier ScienceDirect, IEEE~Xplore,
Springer Link, or Wiley Online Library is technically brittle (anti-bot protections,
CAPTCHAs, dynamic JavaScript rendering, IP-based rate limits) and legally
questionable, as most platforms explicitly prohibit automated access in their terms of
service.

Instead, the pipeline uses \textbf{OpenAlex}
(\url{https://openalex.org}), a free and openly licensed catalogue of more than 250
million scholarly works. OpenAlex aggregates records from Crossref, PubMed, DOAJ,
Unpaywall, and all major publishers, and exposes a public REST API that requires no
registration or API key. Supplying a contact e-mail address in the request headers
places the client in the faster ``polite pool'', which receives priority and more
stable rate limits. The API returns structured JSON with rich metadata including DOI,
title, venue, open-access status, and---crucially for text-based
classification---abstracts encoded as inverted indices.

\subsection{Abstract encoding and reconstruction}

OpenAlex distributes abstracts in an \emph{inverted-index} format for licensing
reasons: rather than providing the plain text, it provides a mapping from each
distinct word to the list of character positions at which that word appears in the
original text. To reconstruct the readable abstract, the pipeline collects all
(position, word) pairs from the inverted index, sorts them in ascending order of
position, and concatenates the words separated by single spaces. This procedure is
lossless for the vocabulary and word order; only whitespace formatting details (e.g.\
multiple spaces or line breaks within the original text) may differ from the source.

When OpenAlex does not hold an abstract for a given work---which occurs for a
substantial fraction of conference papers, theses, and older journal articles---the
abstract field is left empty and the record is flagged as lacking abstract coverage.
Such records still contribute to the metadata corpus and are included in all
year-based counts, but they are excluded from the text-based classification steps
(rule-based and LLM), which require readable text to operate.

% ------------------------------------------------------------------ %
\section{Search strategy}
% ------------------------------------------------------------------ %

The search is structured around 22 exact-phrase queries issued against the combined
title-and-abstract field of OpenAlex. An exact-phrase query requires the words to
appear in the specified order and adjacently (or with standard stop-word gaps) in the
indexed text, yielding high precision. The phrase list is organised in three groups:

\paragraph{Core CARP.} Three broad phrases anchor the search on the problem and its
most common abbreviated forms:
\begin{itemize}[nosep]
  \item ``capacitated arc routing problem''
  \item ``capacitated arc routing''
  \item ``arc routing problem''
\end{itemize}

\paragraph{Structural variants.} Eleven phrases targeting named variants that may not
always be indexed under the full CARP name:
\begin{itemize}[nosep]
  \item ``periodic capacitated arc routing''
  \item ``stochastic arc routing''
  \item ``mixed capacitated arc routing''
  \item ``multi-depot arc routing''
  \item ``multi-objective arc routing''
  \item ``split delivery arc routing''
  \item ``time-dependent arc routing''
  \item ``min-max capacitated arc routing''
  \item ``large-scale capacitated arc routing''
  \item ``windy arc routing''
  \item ``open capacitated arc routing''
\end{itemize}

\paragraph{Methodology phrases.} Eight phrases that combine the arc-routing context
with a specific algorithmic family, ensuring that methodological papers written with
an algorithmic focus rather than a problem-definition focus are also retrieved:
\begin{itemize}[nosep]
  \item ``arc routing metaheuristic''
  \item ``arc routing heuristic''
  \item ``arc routing genetic algorithm''
  \item ``arc routing memetic algorithm''
  \item ``arc routing ant colony''
  \item ``arc routing tabu search''
  \item ``arc routing exact algorithm''
  \item ``arc routing branch and cut''
\end{itemize}

Results from all 22 queries are pooled and \textbf{de-duplicated by the OpenAlex
work identifier}, so each article appears at most once regardless of how many phrases
matched it. In practice the two broadest phrases (\emph{arc routing problem} and
\emph{capacitated arc routing}) subsume the majority of the records retrieved by
the narrower variant and methodology phrases, which typically contribute few net-new
records.

\subsection{Pagination}

OpenAlex paginates results in pages of up to 200 works, using a cursor-based scheme:
each response contains a \texttt{next\_cursor} token that the following request must
supply. The pipeline follows this chain until no further cursor is returned, thus
retrieving the complete result set for each phrase. A short courtesy delay is
observed between consecutive requests to avoid overloading the API.

% ------------------------------------------------------------------ %
\section{Retrieved fields}
% ------------------------------------------------------------------ %

For every unique work the following metadata fields are extracted from the OpenAlex
JSON response and stored:

\begin{center}
\begin{tabular}{@{}p{4.2cm}p{9.5cm}@{}}
\toprule
\textbf{Field} & \textbf{Description and source within the OpenAlex record} \\
\midrule
DOI & Digital Object Identifier (normalised, scheme prefix stripped). \\
Title & Display name of the work. \\
Abstract & Plain text reconstructed from the abstract inverted index (see
           Section~2.1); empty when no abstract is available. \\
Publication year & Calendar year of publication. \\
Venue & Name of the journal or conference series where the work appeared. \\
Publisher & Name of the host organisation (publisher) of the venue. \\
Open-access status & Boolean flag (\emph{is\_oa}) indicating whether the work is
                     freely readable. \\
OA type & Open-access route: gold, green, hybrid, bronze, or closed. \\
Work type & Record category as assigned by OpenAlex: journal article, conference
            paper, preprint, book chapter, etc. \\
Cited-by count & Number of citing works recorded in OpenAlex at retrieval time. \\
OpenAlex identifier & Persistent internal identifier of the form \texttt{W\ldots},
                      used for de-duplication. \\
\bottomrule
\end{tabular}
\end{center}

% ------------------------------------------------------------------ %
\section{Collection results}
% ------------------------------------------------------------------ %

The unfiltered query returned \textbf{905 unique works} spanning from 1969 to 2026.
The presence of records dated before 1981---the year in which the CARP was formally
introduced by Golden and Wong---is explained by two factors: (i) a small number of
mis-dated records in the OpenAlex index, and (ii) works on predecessor problems such
as the Chinese Postman Problem and the Rural Postman Problem, which share the
\emph{arc routing} vocabulary. Of the 905 records, approximately 79\% carry a DOI,
61\% include a usable abstract, and 35\% are open access. The most frequent venues
are \emph{Computers \& Operations Research}, the \emph{European Journal of
Operational Research}, and \emph{Networks}. Missing abstracts and DOIs reflect
coverage gaps in the source data rather than failures of the retrieval procedure.

\subsection{Restriction to recent literature (2021 onward)}

Because the pre-2021 portion of the corpus includes many records without abstracts
(older journals, conference proceedings) and a non-trivial fraction of spuriously
dated or only tangentially related records, the main analysis focuses on the
\textbf{2021--2026 subset}. Filtering is performed on the already-collected data
without re-querying OpenAlex or re-running any classification. The filtered subset
contains \textbf{206 works}: 44 in 2021, 55 in 2022, 30 in 2023, 26 in 2024, 31
in 2025, and 20 in 2026. Of these, 135 carry a usable abstract and are therefore
covered by the LLM classification; 113 of the 206 are open access.

% ------------------------------------------------------------------ %
\section{Rule-based classification}
% ------------------------------------------------------------------ %

The first classification stage uses a deterministic, keyword-driven tagger. For each
article the title and abstract are concatenated into a single text string, and the
following four taxonomies are applied through word-boundary regular expressions
(case-insensitive, except for acronyms written in all-capitals):

\subsection{CARP variant taxonomy}

The tagger recognises 19 structural categories. The category is assigned whenever any
of the specified keywords or acronyms appears in the text. Multiple categories can be
assigned simultaneously when an article addresses a combination of variants (e.g.\ a
multi-depot CARP with time windows). If no variant keyword is detected, the article is
labelled \emph{Classical CARP / unspecified}.

\begin{longtable}{@{}p{4.5cm}p{9.5cm}@{}}
\toprule
\textbf{Category} & \textbf{Trigger keywords / acronyms} \\
\midrule
\endhead
Periodic (PCARP) &
  ``periodic (capacitated) arc routing''; acronym PCARP. \\
Stochastic &
  ``stochastic (capacitated) arc routing''; ``stochastic demand''; acronym SCARP. \\
Uncertain / Fuzzy / Robust &
  ``fuzzy''; ``robust''; ``uncertainty''; ``chance-constrain''. \\
Mixed (MCARP) &
  ``mixed (capacitated) arc routing''; acronym MCARP. \\
Multi-depot &
  ``multi-depot'' (with or without hyphen); ``multiple depots''. \\
Multi-objective &
  ``multi-objective''; ``bi-objective''; ``pareto''. \\
Min-max / Balanced &
  ``min-max''; any form of ``balanc'' (balance, balanced, balancing). \\
Split delivery &
  ``split-delivery''; ``split-demand''. \\
Time-dependent / Dynamic &
  ``time-dependent arc routing''; ``dynamic arc routing''; ``online arc routing''. \\
Time windows (CARPTW) &
  ``time window''; acronym CARPTW. \\
Windy (WARP) &
  ``windy rural postman''; ``windy arc routing''; ``windy postman''; ``windy''. \\
Open (OCARP) &
  ``open (capacitated) arc routing''; acronym OCARP. \\
Prize-collecting / Profitable &
  ``prize-collecting''; ``profitable''; ``team orienteering arc''. \\
Large-scale &
  ``large-scale'' (with or without hyphen). \\
Intermediate facilities (IF) &
  ``intermediate facilit''; ``multiple trips''; ``replenish''; acronym IF (not
  followed by a letter). \\
Green / Electric &
  ``green'' (as adjective); ``electric vehicle''; ``emission''; ``CO2'';
  ``low-carbon''. \\
Node / General routing (GRP) &
  ``general routing problem''; ``node, edge'' (combination); acronym GRP. \\
Rural postman (RPP) &
  ``rural postman''; acronym RPP. \\
Chinese postman (CPP) &
  ``chinese postman''; acronym CPP. \\
\bottomrule
\end{longtable}

\subsection{Exact-method taxonomy}

Eight families of exact or mathematical optimisation methods are detected:

\begin{longtable}{@{}p{4.5cm}p{9.5cm}@{}}
\toprule
\textbf{Category} & \textbf{Trigger keywords} \\
\midrule
\endhead
Branch-and-cut &
  ``branch-and-cut''; ``branch-cut''. \\
Branch-and-price &
  ``branch-and-price''; ``branch-price''. \\
Branch-and-bound &
  ``branch-and-bound''; ``branch-bound''. \\
Column generation &
  ``column generation''. \\
Cutting plane &
  ``cutting-plane''. \\
Integer / linear programming &
  ``integer (linear) program''; ``linear program''; ``mathematical program'';
  acronyms MILP, MIP, ILP. \\
Dynamic programming &
  ``dynamic programming''. \\
Lagrangian relaxation &
  ``lagrang'' (matches Lagrangian, Lagrange relaxation, etc.). \\
\bottomrule
\end{longtable}

\subsection{Constructive-heuristic taxonomy}

Six families of classical constructive heuristics known from the arc routing
literature are detected:

\begin{longtable}{@{}p{4.5cm}p{9.5cm}@{}}
\toprule
\textbf{Category} & \textbf{Trigger keywords} \\
\midrule
\endhead
Path-scanning &
  ``path-scanning''. \\
Augment-merge &
  ``augment-merge''; ``augment-insert''. \\
Construct-strike &
  ``construct-strike''. \\
Ulusoy split / route-first &
  ``ulusoy''; ``route-first''; ``split procedure''. \\
Savings algorithm &
  ``savings algorithm''; ``savings heuristic''; ``savings-based''. \\
Greedy / Nearest neighbour &
  ``greedy''; ``nearest-neighbour''. \\
\bottomrule
\end{longtable}

\subsection{Metaheuristic taxonomy}

Seventeen metaheuristic families are detected. Several families are identified by
both their full name and their widely used acronym:

\begin{longtable}{@{}p{5.2cm}p{8.8cm}@{}}
\toprule
\textbf{Category} & \textbf{Trigger keywords / acronyms} \\
\midrule
\endhead
Genetic / Evolutionary algorithm &
  ``genetic algorithm''; ``evolutionary algorithm''; ``evolutionary computation'';
  ``genetic programming''; acronym GA. \\
Memetic algorithm &
  ``memetic''. \\
Ant colony optimisation (ACO) &
  ``ant colony''; ``ant system''; acronym ACO. \\
Tabu search &
  ``tabu search''; ``tabu''. \\
Simulated annealing &
  ``simulated annealing''. \\
Variable neighbourhood search (VNS) &
  ``variable neighbourhood'' (British or American spelling); acronyms VNS, VND. \\
Particle swarm optimisation (PSO) &
  ``particle swarm''; acronym PSO. \\
GRASP &
  ``greedy randomized adaptive''; acronym GRASP. \\
Iterated local search (ILS) &
  ``iterated local search''; acronym ILS. \\
Guided local search &
  ``guided local search''. \\
Scatter search / Path relinking &
  ``scatter search''; ``path-relinking''. \\
Estimation of distribution (EDA) &
  ``estimation of distribution''; acronym EDA. \\
Artificial bee colony (ABC) &
  ``artificial bee colony''; ``bee colony''; ``ABC algorithm''. \\
Differential evolution (DE) &
  ``differential evolution''. \\
Large neighbourhood search (LNS/ALNS) &
  ``large neighbourhood'' (British or American spelling); acronyms ALNS, LNS. \\
Hyper-heuristic &
  ``hyper-heuristic''. \\
Cooperative / Swarm (other) &
  ``firefly''; ``cuckoo''; ``grey wolf''; ``harmony search''; ``water flow'';
  ``immune algorithm''; ``bacterial''; acronym ABC (general usage). \\
\bottomrule
\end{longtable}

\subsection{Solution-approach assignment and hybrid detection}

Based on the detected method families, each article is assigned a single high-level
\emph{solution approach} label following a priority hierarchy. An article is first
tested for the \emph{hybrid} condition; if it is not hybrid, the remaining categories
are tested from most to least specific:

\begin{enumerate}
  \item \textbf{Hybrid / Matheuristic.} Assigned when the text contains an explicit
        hybrid or matheuristic signal (keywords ``hybrid'', ``matheuristic'',
        ``math-heuristic'', ``cooperative'', or ``memetic''), \emph{or} when the
        article combines at least one exact method with at least one metaheuristic
        (a matheuristic configuration), \emph{or} when two or more distinct
        metaheuristic families are detected simultaneously.
  \item \textbf{Metaheuristic.} Assigned when at least one metaheuristic family is
        detected and the hybrid condition is not met.
  \item \textbf{Constructive heuristic.} Assigned when at least one constructive
        heuristic family is detected and neither of the above applies.
  \item \textbf{Exact.} Assigned when at least one exact method is detected and none
        of the above applies.
  \item \textbf{Generic heuristic.} Assigned when the text contains generic
        algorithmic vocabulary---``heuristic'', ``local search'',
        ``neighbourhood search'', ``metaheuristic''---but no specific family is
        identified.
  \item \textbf{Unspecified.} Assigned when no method-related keyword is found (e.g.\
        purely theoretical papers or those that only have a title available).
\end{enumerate}

Because the rule-based tagger matches every keyword present in the text, it may
over-label survey-style abstracts that enumerate multiple methods without proposing
any of them. It is therefore treated as a fast, transparent first pass that supports
exploratory analysis but should not be used as the sole source for precision
classification.

% ------------------------------------------------------------------ %
\section{LLM semantic classification}
% ------------------------------------------------------------------ %

To overcome the over-labelling tendency of the rule-based tagger and to incorporate
deeper semantic understanding, each article with an available abstract is
re-classified by a large language model (Anthropic Claude). Unlike the rule-based
pass, the LLM assigns \emph{one} primary variant and \emph{one} primary solution
approach per article, reflecting the model's judgement about which label best
describes the central contribution of the paper.

\subsection{Input and scope}

Of the 905 collected works, 552 (61\%) have a usable abstract; only these are
submitted to the LLM, since the model requires readable text to reason over.
Articles without an abstract are excluded from LLM classification and are flagged
accordingly in the output files. The input supplied to the model for each article
consists of the article's title and up to the first 800~characters of its abstract
(sufficient to capture the problem statement and method description in most cases).

\subsection{Classification schema}

The LLM is asked to populate a structured output schema with six fields per article:

\begin{center}
\begin{tabular}{@{}p{4.2cm}p{9.5cm}@{}}
\toprule
\textbf{Field} & \textbf{Description and permitted values} \\
\midrule
Relevance &
  One of: \emph{Core CARP} (the paper addresses the standard CARP directly);
  \emph{CARP variant} (addresses a named extension of the CARP);
  \emph{Related arc routing} (arc routing problem other than CARP, e.g.\ RPP, CPP,
  Windy Postman); \emph{Not relevant} (the paper was retrieved by the search phrases
  but does not substantially address arc routing). \\
Variant &
  A single label from a closed vocabulary of CARP variants (e.g.\ Classical CARP,
  Periodic, Stochastic, Multi-depot, Time windows, Green/Electric, etc.); the label
  that best describes the paper's primary contribution. \\
Approach &
  A single high-level label: \emph{Exact}, \emph{Constructive heuristic},
  \emph{Metaheuristic}, \emph{Hybrid / Matheuristic}, \emph{Machine learning},
  or \emph{Survey / Theoretical / Modelling}. \\
Metaheuristics &
  A list of the specific metaheuristic families named in the text (e.g.\ [``Genetic
  algorithm'', ``Variable neighbourhood search'']); empty when the approach is not
  metaheuristic. \\
Is hybrid &
  Boolean: \texttt{true} when the paper combines two or more distinct algorithmic
  families (exact + metaheuristic, or multiple metaheuristics). \\
How solved &
  A single English sentence summarising how the problem was solved, written at an
  abstract level (e.g.\ ``A genetic algorithm with adaptive large neighbourhood
  search is combined with an integer programming model for the lower bound''). \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Advantages over rule-based classification}

The LLM classification offers several advantages over the keyword tagger:

\begin{itemize}[nosep]
  \item \textbf{Single primary label.} The LLM assigns only one variant and one
        approach, which eliminates spurious multi-labelling when a survey abstract
        cites many methods.
  \item \textbf{Semantic inference.} The model can infer the method from paraphrases
        and indirect descriptions that do not contain the exact keywords used in the
        taxonomy (e.g.\ ``we solve the relaxed formulation and improve with local
        moves'' is correctly labelled as \emph{Hybrid / Matheuristic}).
  \item \textbf{Relevance filtering.} The model explicitly identifies records that are
        not about arc routing, providing a clean relevance filter for all downstream
        analyses.
  \item \textbf{How-solved summary.} The one-sentence summary captures the
        methodological essence of each paper in a form directly usable in a literature
        review.
\end{itemize}

% ------------------------------------------------------------------ %
\section{Analysis}
% ------------------------------------------------------------------ %

The final stage builds on the LLM-classified corpus. Records labelled \emph{Not
relevant} by the LLM are excluded from all thematic analyses (variant and method
distributions) but are retained in total-count statistics. The following outputs are
produced:

\begin{itemize}[nosep]
  \item \textbf{Publications per year.} A bar chart of the number of collected works
        per calendar year, covering the range 1981--2026 for the full corpus and
        2021--2026 for the focused subset.
  \item \textbf{CARP variant distribution.} A horizontal bar chart ranking variants by
        frequency of appearance in the LLM-classified corpus.
  \item \textbf{Solution approach distribution.} A horizontal bar chart of the
        six high-level approach categories.
  \item \textbf{Metaheuristic families.} A horizontal bar chart of the 15 most
        frequently named specific metaheuristic families.
  \item \textbf{Open-access share.} A horizontal bar chart comparing the fraction of
        open-access versus closed-access records in the corpus.
  \item \textbf{Evolution of approaches over time.} A stacked bar chart showing the
        yearly composition of solution approaches from 2005 onward, revealing shifts
        in the field's methodological preferences.
  \item \textbf{Variant $\times$ approach cross-tabulation.} A matrix counting the
        co-occurrence of each CARP variant (rows) with each solution approach
        (columns), exported as a CSV file for further analysis.
\end{itemize}

All figures for the 2021-onward subset are generated independently from those for
the full corpus and are stored with a \texttt{2021on\_} filename prefix to avoid
confusion.

% ------------------------------------------------------------------ %
\section{Reproducibility and limitations}
% ------------------------------------------------------------------ %

\subsection{Reproducibility}

The pipeline is fully reproducible from an internet-connected machine: it queries only
a public API, performs no manual curation steps, and applies deterministic
transformations at every stage (except the LLM call, which is non-deterministic but
statistically stable across runs). All intermediate files (JSON, CSV) are version-controlled
alongside the code, so the analysis figures and cross-tabulations can be regenerated
at any time without re-querying OpenAlex.

\subsection{Coverage limitations}

OpenAlex does not index every journal or conference. Coverage is particularly uneven
for older proceedings, regional journals, and theses. The 39\% of records without an
abstract most likely reflects this coverage gap rather than the true proportion of
CARP papers published without abstracts.

\subsection{Rule-based classifier limitations}

The rule-based classifier operates solely on surface-form text. It will miss relevant
papers that use non-standard terminology and will over-label survey papers that
enumerate many methods in their abstracts. The LLM classification mitigates these
issues, but it is in turn limited to records that have an abstract available.

\subsection{Temporal scope}

The API was queried once at a fixed point in time. OpenAlex continuously ingests new
records, so the corpus will grow stale over time. Re-running the collection step with
the same search phrases and de-duplicating against the existing records would extend
the corpus incrementally without discarding prior classifications.

\end{document}
